Linear instability underlying synchronous waving of marine grass in flow

### 2014-09-06 Paper/grass.tex
Reynolds section update

A threshold in $\Rey$ for the onset of the instability naturally emerges from the solution of \eqref{Orr-somerfield}. 
The primary reason for the existence of critical $\Rey$ is the presence of dissipation of flow instability 
due to grass drag. Indeed a calculation undertaken for terrestrial grass shows the suppression of growth rate of instability
due to grass drag\cite{Delangre06}. It is important to notice the absence of a threshold condition in the previous analysis of 
free shear flow with various assumptions about mean flow profile and the role of grass drag\cite{Raupach96,Delangre06}.
The dependence of this critical $\Rey$, and the corresponding fastest growing wavenumber $k$, 
on the $\delta/H$ and $\hg/H$ is shown in figure \ref{Re_vs_delta}, and compared with experimental observation of the 
threshold\cite{Ghisal02}.

>>>>

A threshold in $\Rey$ for the onset of the instability naturally emerges from the solution of \eqref{Orr-somerfield}. 
The primary reason for the existence of critical $\Rey$ is the presence of dissipation of flow instability 
due to grass drag. Indeed a calculation undertaken for terrestrial grass shows the suppression of growth rate of instability
due to grass drag\cite{Delangre06}. Absence of threshold in the previous analysis can be attributed to the assumptions such 
as approximationn of mean flow with the free shear layer profile and the exclusion of grass drag in the stability analysis \cite{Raupach96,Delangre06}.
The dependence of this critical $\Rey$, and the corresponding fastest growing wavenumber $k$, 
on the $\delta/H$ and $\hg/H$ is shown in figure \ref{Re_vs_delta}, and compared with experimental observation of the 
threshold\cite{Ghisal02}.
